A Failure Detection Approach of Data Center Networks\titlenote{(Produces the permission block, and copyright information). For use with SIG-ALTERNATE.CLS. Supported by ACM.}

### 2016-06-28 SIG Proceedings Template-Jan2015 Zip/paper.tex
continue writing my paper

\item \textbf{Non-imperative Device.} It includes other routers and switches. A single failure of a link or a router does not affect the functionality of a data center because of path redundancy. So administrators care more about how effective the detect service is (The ability to identify actually happening failures).

@@

Figure 2 illustrates the entire architecture of our failure detection system. It mainly contains two modules. The servers failure detection system is autonomous and combines centralized structure with decentralized structure. A server can both play the role of a detector and a monitored object. Each server is monitored by multiple FD processes installed on different servers for redundancy. A server can also monitor a group of servers. Once the FD outputs the crash of a server, it will send a crash report message to \textbf{Crash Decider}. \textbf{Crash Decider} will determine the final status of this server.

@@

To collect required traffic data, we simply install \textit{tcpdump} on each router and switch. These data will be sent to \textbf{Traffic Analysis Worker} for further analysis.

@@

\paragraph{Feature Extraction}
The first step is to extract reasonable features from raw traffic data. To address this issue, we extract $m^2$ features, each of which denotes traffic of one direction. Because there are $m$

>>>>

\item \textbf{Non-imperative Device.} It includes links, other routers and switches. A single failure of a link or a router does not affect the functionality of a data center because of path redundancy. So administrators care more about how effective the detect service is (The ability to identify actually happening failures).

@@

Figure 2 illustrates the entire architecture of our failure detection system. It mainly contains two modules. The servers failure detection system combines centralized with decentralized structures. A server can both play the role of a detector and a monitored object. Each server is monitored by multiple FD processes installed on different servers for redundancy. A server can also monitor a couple of servers. Once the FD outputs the crash of a server, it will send a crash report message to \textbf{Crash Decider}. \textbf{Crash Decider} will determine the final status of this server.

@@

To collect required traffic data, we simply install \textit{tcpdump} on each router and switch. These data will be collected to \textbf{Traffic Analysis Worker} for further analysis.

@@

\paragraph{Feature Extraction}
The first step is to extract reasonable features from raw traffic data. To address this issue, we extract $n^2$ features, each of them denotes traffic of one direction where $n$ denotes the number of racks. Obviously, for each rack, there are $n$ different traffic directions (each one corresponds to one rack), so there are $n^2$ directions in total. Formally, the traffic feature during a time period
